In the next steps you will get Introduction how to bring an existing roboter-\/setup to life.\hypertarget{page1_step1}{}\section{Step1\-: Power on the Robot}\label{page1_step1}
First you may \hyperlink{page1_checkWires}{Troubleshooting\-: Check the Wires}. To power on the robot afterwards, you had to press the green button (see \hyperlink{index_hw_setup}{The Hardware Setup}). The switches 1 (E\-P\-O\-S2) and 2 (Laserscanner) right of the power button should be switched on.\hypertarget{page1_step2}{}\section{Step2\-: Waiting until the robot is ready}\label{page1_step2}
Some L\-E\-Ds are switch on others are off. If the robot get not into this state within 5 minutes lock at \hyperlink{page1_checkLEDs}{Troubleshooting\-: The Meaning of the L\-E\-Ds}.\hypertarget{page1_step3}{}\section{Step3\-: Drive the robot}\label{page1_step3}
There are different driving-\/\-Modes by using the gamepad. When the robot doesn't move, you can switch between this modes by pressing the \char`\"{}\-R\-B\char`\"{}-\/\-Button of the Logitech F710. For other gamepads it's the .... button.\hypertarget{page1_mode_tank}{}\subsection{driving-\/mode\-: One Stick for each side}\label{page1_mode_tank}
With the left stick you set the velocity for the left side of the robot and with the right stick for the right side of the robot.\hypertarget{page1_mode_twostick}{}\subsection{driving-\/mode\-: Velocity and Turning with two sticks}\label{page1_mode_twostick}
The right Stick (only up and down) set the forward velocity and the left stick (only left and right) set the angular velocity of the robot.\hypertarget{page1_mode_onestick}{}\subsection{driving-\/mode\-: Velocity and Turning with one stick}\label{page1_mode_onestick}
Same as \hyperlink{page1_mode_twostick}{driving-\/mode\-: Velocity and Turning with two sticks} but both directions (up -\/ down \& left -\/ right) are set with one stick.\hypertarget{page1_power_off}{}\section{Last Step\-: Power off the robot}\label{page1_power_off}
After driving you can power off the robot by press and hold the red power button until the Lights of the Power-\/panel are switched off.\hypertarget{page1_checkWires}{}\section{Troubleshooting\-: Check the Wires}\label{page1_checkWires}
The Controll-\/\-P\-C (see \hyperlink{index_hw_setup}{The Hardware Setup}) should be connected to one of the E\-P\-O\-S2s and to the Laser-\/\-Scanner. Both are connected by U\-S\-B. The \char`\"{}\-Nano Receiver\char`\"{} of the Controller (Logitech F710) should also Plugged into one U\-S\-B-\/\-Port.\hypertarget{page1_checkLEDs}{}\section{Troubleshooting\-: The Meaning of the L\-E\-Ds}\label{page1_checkLEDs}
Here some known L\-E\-D-\/settings, the corresponding errors and their solution.\hypertarget{page1_no_connection}{}\subsection{L\-E\-D\-: red is on}\label{page1_no_connection}
Power off the robot (\hyperlink{page1_power_off}{Last Step\-: Power off the robot}), \hyperlink{page1_checkWires}{Troubleshooting\-: Check the Wires}, and switch on again (\hyperlink{page1_step1}{Step1\-: Power on the Robot}). 